\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-26 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Figure 7

\begin{figure}[htbp]
\caption{Histogram of the share of additive costs in total costs (restricted sample)}
\label{fig:histogram_beta_robustness}
\begin{center}
\begin{tabular}{cc}
\multicolumn{2}{c}{Air transport} \\
{\small (a) Separability (baseline)} & {\small (b) Non-separability}\\
\includegraphics[width=7cm, height=5cm]{Etude_beta_pond_sitc2separe_air.pdf}
& \includegraphics[width=7cm, height=5cm]{Etude_beta_pond_sitc2ns_air.pdf} \\
\multicolumn{2}{c}{Maritime transport} \\
{\small (c) Separability (baseline)} & {\small (d) Non-separability}\\
\includegraphics[width=7cm, height=5cm]{Etude_beta_pond_sitc2separe_ves.pdf}
& \includegraphics[width=7cm, height=5cm]{Etude_beta_pond_sitc2ns_ves.pdf} \\
\multicolumn{2}{l}{{\footnotesize Notes: Distribution of $\beta_{ikt}$ over the triplet (year-product-country), weighted by share of yearly value of flow.}}\\
\end{tabular}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Histogram of the share of additive costs in total costs (restricted sample)}
\label{fig:histogram_beta_robustness}
\begin{center}
\begin{tabular}{cc}
\includegraphics[width=14cm, height=10cm]{Etude_beta_pond.jpg}\\
\multicolumn{2}{l}{{\footnotesize Notes: Distribution of $\beta_{ikt}$ over the triplet (year-product-country), weighted by share of yearly value of flow.}}\\
\end{tabular}
\end{center}
\end{figure}
